---
title: "Analysis of Department of Mechanical Engineering Output"
author: "Alison Henry"
date: "20/11/2019"
output:
  html_document:
    toc: yes
  html_notebook:
    theme: lumen
    toc: yes
  prettydoc::html_pretty:
    theme: hpstr
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rscopus)
library(tidyverse)
library(bibliometrix)
library(prettydoc)
```
# Bibliographic Collection
**Data source**:   Scopus (http://www.scopus.com)

**Document Type**: Articles, letters, review and proceedings papers

**Authors**: Author names taken from the University of Alberta Department of Mechanical Engineering Website

**Query date**:    November, 2019

## Data load

```{r data retrieval, include=FALSE}
## Set your API key
set_api_key("875146d79ec70b39b9fcbc099b07e321")

## Read in our list of authors
mecenames <- read.csv("mecenames.csv", header = TRUE)

## add in a column for the affiliatiomn
mecenames$affiliation <- "alberta"

## Get the Scopus IDs of these authors
## for this function we need the API key as a variable
api_key = get_api_key()
mece_authors <- idByAuthor(mecenames, api_key)

## Normally: replace any missing IDs
## For today's purposes, we will create our ID vector by omitting the missing IDs
id <- mece_authors$id[!is.na(mece_authors$id)]

## Download the bnibliographic collection for these authors
papers <- retrievalByAuthorID(id = id, api_key = api_key)
M <- papers$M
```
From our list of author names, we used the Scopus API to retrieve Researcher IDs, then made another API call to download the documents associated with these IDs. This resulted in a set of `r length(M)` de-duplicated papers. 

## Main findings about the collection

Let's take a look at the summary of findings about this collection, including average numbers of publications per author and citations per publication. 

```{r Descriptive Analysis, echo=TRUE, comment=NA}
#options(width=160)
results <- biblioAnalysis(M)
summary(results, k=10, pause=F, width=130)
plot(x=results, k=10, pause=F)
```

## Most Cited References

These are the most frequently cited manuscripts in this collection.
```{r Most cited references,  comment=NA}
CR <- citations(M, field = "article", sep = ";")
cbind(CR$Cited[1:20])
```
